Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 4

    The comparison confirms that \minn{} should be reasonable proxy of the 
    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
    Chabrier IMF; but there are still differences in median \mstar{} and 
    details in the \m2l{} estimates}.  
    More importantly, it shows that the \mden{} profile at 
    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
    to the ``in-situ'' processes.

    We also compare with a uniquely massive BCG at high redshift: 
    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
    $z{\sim} 1.1$ (\citealt{Liu2013}).  
    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
    This unique object may present an interesting case where the inner ``core'' of a 
    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
    under construction.
    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
    process, and help us confirm whether the environmental dependence of structure 
    has already emerged within massive galaxies at higher redshift 
    (e.g. \citealt{Papovich2012})

    % TODO: Comparison with Illustris.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{What is the ``Total Mass'' of Massive Galaxies?}

    Even with deep HSC images, it is non trivial to clearly define and measure the
    ``total'' \mstar{} for these massive systems. 
    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
    over the 2-D modeling method and in principle, should capture a the majority of 
    the stellar mass. 
    However, even though we extend to 100 kpc, there is no evidence that the profile 
    drops to zero on these scales. 
    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
    For this, we integrate the \mden{} profiles out to the detection limit in 
    surface brightness profile that is defined by the background noise.
    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
    difference of about ${\sim}0.04$ dex. 
    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
    and \mmax{}. 
    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
    of the stellar envelope. 
    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
    uncertainty on \mmax{} is larger. 
    However, we have checked that none of our results are changed by replacing \mtot{} 
    via \mmax{}.

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2017}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
            The total luminosity is based on 2-D \texttt{SerExp} models 
            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
            The \m2l{} is also from SED fitting assuming a Chabrier IMF.

        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
            \citep{Leauthaud2016} where the \mstar{} is derived using 
            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
            \texttt{S82}.

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

    Finally, we emphasize that in this present study we do not attempt to separate the 
    light of the galaxy with a potential (and distinct) ``intra-cluster''
    light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
    Mihos2005}). 
    Instead, we adopt the view that the light of the main galaxy and the 
    ``intra-cluster''component are a smooth and continuous distribution. 
    A reliable isolation of a physically meaningful ICL component using photometry 
    alone is extremely difficult, if not impossible. 
    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
    an ``inner component'' and an ``intra-cluster'' component. 
    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
    evidence for a distinct secondary component. 
    We do note however, that our \rbcg{} sample contains only a small fraction of 
    extremely massive clusters where strong evidence of photometric ICL component is 
    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
    ICL only becomes important outside that radius and is dominated by individual 
    tidal features. {\bf I continue to think you are saying all gals have some ICL, rather 
    that no galaxies have ICL...}

>>>>

    We also compare with a uniquely massive BCG at high redshift: 
    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
    $z{\sim} 1.1$ (\citealt{Liu2013}).  
    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
    massive galaxies nicely inside 10-15 kpc, but becomes steeper in the outskirt.
    It represents an interesting phase where the inner ``core'' of massive BCG is 
    already in pace at $z{\sim} 1$ while the outer halo is still being assembled.

    These comparisons certainly support the idea that \minn{} mainly consists of 
    \textit{in-situ} stars and mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
    component.     
    Meanwhile, they also show that the \texttt{in-situ} component 
    could have steeper \mden{} slope and mass distribution much more extended than 
    10 kpc\footnote{We convert these \mden{} profiles to the same 
    Chabrier IMF; but there are still differences in median \mstar{} and 
    details in the \m2l{} estimates}. 
    More comparisons with massive galaxies at high redshift and simulated 
    \textit{in-situ} components will help shed light on this.

    In line with the prediction from Illustris, this comparison also 
    suggests that, at very high-mass end, the accreted component can make significant 
    contribution even within the inner 10--20 kpc. 
    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
    more attention. 
    It is possible that they mainly come from major merger and used to be the 
    \texttt{in-situ} component of another massive galaxy. 
    It would be interesting see whether there is an alternative, but also physically 
    motivated definition of \textit{in-situ} component that can be more easily examined 
    by observation.

    % TODO: Move to Paper II
    %More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
    %process, and help us confirm whether the environmental dependence of structure 
    %has already emerged within massive galaxies at higher redshift 
    %(e.g. \citealt{Papovich2012})

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Stellar Halo or Intra-cluster Light?}

    Finally, we emphasize that in this work we do not attempt to separate the 
    potential (and distinct) ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from the massive 
    galaxies. 
    Instead, we adopt the view that the light of the main galaxy and the 
    ``intra-cluster''component share a smooth and continuous distribution.

    The majority of massive galaxies in our samples are not considered as BCGs
    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
    an ``inner component'' and an ``intra-cluster'' component. 
    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
    evidence for a distinct secondary component. 
    We do note however, that our \rbcg{} sample contains only a small fraction of 
    extremely massive clusters where strong evidence of photometric ICL component is 
    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
    ICL only becomes important outside that radius and is dominated by individual 
    tidal features.
Reliable isolation of a physically meaningful ICL component using photometry 
    alone is extremely difficult, if not impossible.
